SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-12 response.tex

\textcolor{blue}{We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}. Lines 4 to 6 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds. Lines 7 to 12 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level. Lines 13 to 22 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm. Finally, lines 23 to 25 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.
}

% comment9
\rcomment{
\color{red} Some conditions in Algorithm 2 are unclear, such as "for Client i do", "while Not Converged do", and "for Each point Oj $\neq$ Oi do". Clarification and revision are needed.
}

\textbf{Response:} Thank you for your valuable feedback on Algorithm 2. We have reviewed the conditions and updated the descriptions to ensure they are clear and unambiguous. Specifically:

\textbf{"for Client $i$ do"}: We clarified this condition to indicate that the algorithm iterates over each client in the dataset, specifying how Client $i$ is selected and what actions are taken for each client.

\textbf{"while Not Converged do"}: We revised this condition to include the specific convergence criteria used in the algorithm. This provides a clear stopping condition of $\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$, ensuring that readers understand when the loop will terminate.

\textbf{"for Each point $O_j \neq O_i$ do"}: We clarified that this loop iterates over all points in the dataset except for point $O_i$, and we specified the purpose of comparing each $O_j$ with $O_i$ in the context of the algorithm’s objective.

@@

% 示例和场景：我们增加了说明性示例和场景，展示意图识别在现实世界中的应用，增强读者对其实际应用的理解。

% 与现有模型的比较：为了进一步阐明我们的方法，我们将意图识别的概念与现有模型进行了比较，强调了我们的框架的创新之处和优势。

% 我们感谢您的反馈，这对我们改进这一部分内容有很大帮助。我们相信，这些增强将使读者对我们工作的核心思想——攻击者意图识别有更清晰、更全面的理解。

\textbf{Response:}
Thank you for your insightful comments regarding the concept of intent recognition in our manuscript. We recognize the importance of clearly defining and constructing the notion of attacker intent, as it is a pivotal innovation in our research.

@@

To address your concerns, we have elaborated on the definition of attacker intent in the revised manuscript. Specifically, we now include:

\textbf{Clear Definition}: We provide a concise definition of attacker intent, explaining its relevance in the context of our study and its implications for threat assessment and response strategies.

\textbf{Construction of Intent}: We detail how attacker intent is constructed within our framework, outlining the factors that contribute to its identification. This includes the behavioral patterns, contextual clues, and data-driven approaches used to infer intent.

\textbf{Examples and Scenarios}: We have added illustrative examples and scenarios that demonstrate how intent recognition can be applied in real-world situations, enhancing readers’ understanding of its practical applications.

\textbf{Comparison with Existing Models}: To further clarify our approach, we compare our concept of intent recognition with existing models, highlighting the innovations and advantages of our framework.

@@

% 提供上下文：我们增加了与前文讨论相关的上下文信息，帮助读者理解这些步骤在更广泛框架中的重要性。

% 举例说明：在适用的情况下，我们添加了示例，以说明每个步骤的执行方式，使读者更容易理解所呈现概念的实际应用。

% 这些修改增强了段落的清晰度和可理解性，确保读者能够跟随预期的逻辑，并理解每个步骤在该过程中的重要性。我们非常感谢您的反馈，这对改进手稿的这一部分起到了重要作用。

\textbf{Response:} Thank you for your valuable feedback regarding the third paragraph in the left column on page 9, where several "steps" were mentioned but not sufficiently explained. We acknowledge that the lack of detailed explanations may lead to confusion for readers.
To address this issue, we have revised the paragraph to provide a thorough explanation of each of the four steps related to Long-term Attack Intention Detection. Specifically, we have made the following enhancements:

\textbf{Definition of Each Step:} We have clarified the content of each step, including its purpose and how it fits into the overall process discussed in the manuscript.

\textbf{Providing Context:} We have added contextual information relevant to previous discussions, which helps readers understand the significance of these steps within a broader framework.

\textbf{Illustrative Examples:} Where applicable, we have included examples to illustrate how each step is executed, making it easier for readers to grasp the practical applications of the concepts presented.

These modifications enhance the clarity and comprehensibility of the paragraph, ensuring that readers can follow the intended logic and appreciate the importance of each step in the overall process.
% ---------------------------------------------------------

% Thank you for your observation regarding the mention of several "steps" in the third paragraph of the left column on page 9. We acknowledge that these steps were not adequately explained, which may lead to confusion for the reader. But in fact, these four steps correspond to the four steps of ong term attack intention detection.

% To address this issue, we have revised the paragraph to provide a detailed explanation of each step mentioned. Specifically, we now:

% Define Each Step: We clarify what each step entails, including its purpose and how it fits into the overall process discussed in the manuscript.

% Provide Context: We include contextual information that connects the steps to the preceding discussion, helping readers understand their significance within the broader framework.

% Illustrate with Examples: Where applicable, we have added examples to illustrate how each step is executed, making it easier for readers to grasp the practical application of the concepts presented.

% These modifications enhance the clarity and comprehensibility of the paragraph, ensuring that readers can follow the intended logic and understand the importance of each step in the process. We appreciate your feedback, which has been instrumental in improving this section of the manuscript.

The relevant parts after modifications are as follows:

@@

% 性能保证：该条件还充当性能保证，确保系统能够在指定的时间范围内维持其操作完整性。它有助于平衡资源分配与性能之间的权衡，从而在不影响系统稳定性的情况下实现最佳结果。

% 可扩展性：设置ζT使得优化模型具有可扩展性。它为在不同场景和规模中调整模型提供了方法，确保优化能够有效地应用于各种上下文而不会失去其有效性。

% 我们已修订手稿，以在第V.2节中对该条件提供更详细的解释，增强读者的理解。我们非常感谢您的反馈，这帮助我们提高了工作的可理解性。

\textbf{Response:} Thank you for your insightful question regarding the condition \( \zeta T \) in the optimization problem presented in Section V.2. This condition plays a crucial role in the formulation of the optimization model, and we recognize the need for further clarification.

@@

    \item \textbf{Scalability}: Setting \( \zeta T \) allows for scalability in the optimization model. It provides a way to adapt the model for different scenarios and scales, ensuring that the optimization can be effectively applied in various contexts without losing its validity.
\end{enumerate}

We have revised the manuscript to provide a more detailed explanation of this condition in Section V.2, enhancing clarity for readers. We appreciate your feedback, which has helped us improve the comprehensibility of our work.

The changes are as followings:

\textcolor{blue}{This problem can be abstracted as rays in a high-dimensional space with specific starting points. The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round. The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays. redAmong them, $\ zeta$ is to avoid interference from excessively outlier rays.}

### 2024-11-12 main-v2.tex
archive: 2024.11.5 22:04
《ignore the》

Signed-off-by: LetMeFly666 <814114971@qq.com>

\textbf{Evaluation metrics:}
% 就像其他文章中的评价指标一样，我们使用两个关键指标来评估投毒攻击与防御方法的效果，即ASR（攻击成功率）和 TSR（测试成功率）。ASR表示恶意节点成功诱导全局模型成功预测指定目标的概率。攻击者的目标是最大化ASR，而有效的防御措施则旨在防止ASR上升。TSR表示全局模型在测试集上的预测正确率。攻击者的目标是尽量维持模型的TSR不变，以避免被轻易检测到，而有效的防御措施则不应显著降低全局模型的TSR。
% Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR represents the probability that malicious nodes successfully induce the global model to predict the specified target. The goal of the attacker is to maximize ASR, while effective defense measures aim to prevent an increase in ASR. TSR represents the accuracy of the global model on the test set. The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
\textcolor{red}{For instantaneous attack behavior perception,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target. The attacker aims to maximize the ASR, whereas effective defense mechanisms strive to prevent an increase in ASR. TSR indicates the accuracy of the global model on the test set. The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR. \textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}

\begin{figure*}[!t]
    \centering
    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}

>>>>

\textbf{Evaluation metrics:}
% 就像其他文章中的评价指标一样，我们使用两个关键指标来评估投毒攻击与防御方法的效果，即ASR（攻击成功率）和 TSR（测试成功率）。ASR表示恶意节点成功诱导全局模型成功预测指定目标的概率。攻击者的目标是最大化ASR，而有效的防御措施则旨在防止ASR上升。TSR表示全局模型在测试集上的预测正确率。攻击者的目标是尽量维持模型的TSR不变，以避免被轻易检测到，而有效的防御措施则不应显著降低全局模型的TSR。
% Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR represents the probability that malicious nodes successfully induce the global model to predict the specified target. The goal of the attacker is to maximize ASR, while effective defense measures aim to prevent an increase in ASR. TSR represents the accuracy of the global model on the test set. The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
\textcolor{red}{For instantaneous attack behavior perception,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate). ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target. The attacker aims to maximize the ASR, whereas effective defense mechanisms strive to prevent an increase in ASR. TSR indicates the accuracy of the global model on the test set. The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR. \textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions; ``Rec" stands for recall, representing the model's ability to identify positive instances correctly; ``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; ``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; ``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/lab2-combined.pdf}
    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE. The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa. }
    \label{fig:lab2}
\end{figure*}
